LaMachine: A meta-distribution for NLP software

### 2019-03-21 docs/lamachine_clarin2018.tex
[paper] rephrased 2nd sentence of introduction (was ungrammatical/not understandable)
[paper] added a paragraph to clarify that LaMachine is in widespread use and has been installed by numerous users (rather than just by the author as one reviewer thought)

Software is a key deliverable and a vital component for research in projects such as those under the CLARIN umbrella. Software provides researchers the instruments to yield for their research. It is CLARIN's core mission to make
digital language resources, including software, available to the wider research community.

@@

@@

LaMachine exists since May 2015 and has been used extensively ever since by numerous users. In early 2018 version 2 was
released which was a significant redesign, powered by Ansible\footnote{\url{https://www.ansible.com}}.

>>>>

Software is a key deliverable and a vital component for research in projects such as those under the CLARIN umbrella.
Software can be seen as an invaluable instrument that enable researchers to perform their studies. It is CLARIN's core mission to make
digital language resources, including software, available to the wider research community.

@@

LaMachine exists since since May 2015 and has been installed extensively ever since by numerous users. In early 2018 version 2 was
released which was a significant redesign, powered by Ansible\footnote{\url{https://www.ansible.com}}. We ourselves use
LaMachine as a means by to make our full software stack available to end-users, whether those be individual researchers, research
groups, or hosting providers like CLARIN centres. LaMachine has in fact been adopted in all of those areas. Quantifying its
actual use is not trivial despite having some tracking solutions in place, but can roughly be put at around one or two
installations or upgrades \emph{every day}. We also see a regular influx of questions on our issue tracker, indicating
community interest.

@@
